# `rnorm()`

The function `rnorm()` enables us to generate normally distributed random numbers.

```{r rnorm, eval = FALSE}
rnorm(n, mean = 0, sd = 1)
```

where `n` is the number of random numbers we want to generate,
`mean` is the mean of the normal distribution and
`sd` is the standard deviation.

A function call to get 1000 normal distribution random numbers with mean 10 and standard deviation 2 would be

```{r rnormexp, eval = FALSE}
rnorm(n = 1000, mean = 10, sd = 2) 
```

**Note**: Besides random number generation `R` provides probability distribution functions, density functions and quantile functions
for most of the common distributions. 
The following naming scheme is used:

- p*dist* for probability distribution functions,
- d*dist* for density functions,
- q*dist* for quantile functions,
- r*dist* for random number generation,

where *dist* indicates the desired distribution. 

An overview over the base `R` functionality and distributions provided by additional CRAN packages can be found
[here](https://cran.r-project.org/web/views/Distributions.html).