# Querying Quandl Databases from R Console
As mentioned before you can find codes for datasets directly on the [Quandl website](https://www.quandl.com) 
or you can use the `Quandl.search()` function. 
It has only one mandatory argument `query` which you have to use to enter your search term.
Optional arguments of `Quandl.search()` are 

* `page`: specifies which page of the search results should be returned
* `source`: allows the user to specify a database which should be queried
* `silent`: if set to **FALSE** first three results are printed to the console
* `authcode`: if not set before with `Quandl.auth` function you can enter your API token here

An example call to `Quandl.search()` to find historical data for International Business Machines (IBM) by using
the Yahoo Finance Database is given below.

```{r yahoo}
ibm <- Quandl.search("IBM", source = "YAHOO", silent = TRUE)
```

The API call above returns a list of length 16 where the code needed for `Quandl` function and several other details can be extracted.

```{r yahooibm}
str(ibm)
```