```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
library(Quandl)
Quandl.auth("x81naq-zMUpwM9fzkhYq")
Sys.setlocale(category = "LC_ALL", locale = "en_US.utf8")
# end setup chunk
```

# Downloading Data from Quandl Databases

The workhorse is the `Quandl()` function.
```{r quandlhelp, eval = FALSE}
Quandl(code, type = c("raw", "ts", "zoo", "xts", "timeSeries"), start_date,
  end_date, transformation = c("", "diff", "rdiff", "normalize", "cumul",
  "rdiff_from"), collapse = c("", "daily", "weekly", "monthly", "quarterly",
  "annual"), sort = c("desc", "asc"), meta = FALSE,
  authcode = Quandl.auth(), ...)
```

You can start downloading data by only using the `code` argument.
Codes can be found on the website of [Quandl](https://www.quandl.com) 
or you can query the databases directly within `R`. (see chapter 1.4).
Suppose we want the data for the automobile manufacturer *BMW* from Frankfurt Stock Exchange
using Google Finance as database.

```{r data}
bmw <- Quandl("GOOG/FRA_BMW")
```

```{r data1}
str(bmw)
```

```{r data2}
head(bmw)
```

```{r data3}
tail(bmw)
```

```{r data4}
summary(bmw)
```

# Using additional arguments of `Quandl()` function

The function call `Quandl("GOOG/FRA_BMW")` without any additional arguments returns a data frame
with six columns, namely 'Date', 'Open', 'High', 'Low', 'Close' and 'Volume' for
all available dates. Furthermore, the data frame is returned in descending order.
Our R object `bmw` ranges from `r min(bmw[,1])` to `r max(bmw[,1])`.

If you want to truncate your time series the two arguments `start_date` and `end_date`
of the `Quandl` function can be used.

In a next step, we only want to download the BMW data for 2014 and we want the ordering 
of the data to change from descending to ascending. 
Both arguments `start_date` and `end_date` have to be in the format 'yyyy-mm-dd'.

```{r bmw2014}
bmw_2014 <- Quandl("GOOG/FRA_BMW", start_date = "2014-01-01", end_date = "2014-12-31",
                   sort = "asc")
```

```{r bmw20141}
str(bmw_2014)
```

```{r bmw20142}
head(bmw_2014)
```

Comparing both R objects `bmw` and `bmw_2014` we have reduced the observations for each 
of the columns from `r dim(bmw)[1]` to `r dim(bmw_2014)[1]`.
The dates we have data for range from `r min(bmw_2014[,1])` to `r max(bmw_2014[,1])`.

By default, `Quandl()` returns data as class `data.frame` which is not the best
output type when dealing with time series.

`Quandl()` offers several different output classes,

* data.frame
* ts
* zoo
* xts
* timeSeries,

which can be chosen with `type` argument.

An overview about the different classes and corresponding packages can be found in the 
[CRAN Task View: Time Series Analysis](https://cran.r-project.org/web/views/TimeSeries.html) or
in the pdf [Working with Financial Time Series Data in R](http://faculty.washington.edu/ezivot/econ424/Working%20with%20Time%20Series%20Data%20in%20R.pdf) written by Eric Zivot.

To get an output with class `zoo` the function call would look like this:
```{r bmwzoo}
bmw_2014_zoo <- Quandl("GOOG/FRA_BMW", start_date = "2014-01-01", end_date = "2014-12-31",
                   sort = "asc", type = "zoo")
```

Let's have a look at what the standard `plot` function produces for both classes.
```{r plotcomp}
plot(bmw_2014)
plot(bmw_2014_zoo)
```

First call produces a scatterplot matrix whereas the columns of the data frame are plotted against each other.
Second call returns plotted time series for each column which is more appropriate for our data.

The reason for this behavior is that 'plot' function checks the classes of the objects to be visualized. 
So under the hood for an object with class 'data.frame' the function 'plot.data.frame' from package `graphics` is used
and for objects with class 'zoo' the 'plot.zoo' function in package `zoo`.

Now we have data on a daily basis but `Quandl()` offers several more choices like,

* weekly
* monthly
* quarterly 
* annual,

which can be achived using the `collapse` argument.
By collapsing a daily dataset to weekly,
you will get a sample of the original dataset where the observation for each week
is the last data point available for that week.

To download weekly data of 2014 for BMW equity from Frankfurt Stock Exchange
the function call would be
```{r bmwweek}
bmw_2014_zoo_weekly <- Quandl("GOOG/FRA_BMW",
                             start_date = "2014-01-01", end_date = "2014-12-31",
                             sort = "asc", type = "zoo", collapse = "weekly")
```

```{r bmwweek1}
str(bmw_2014_zoo_weekly)
```

```{r bmwweek2}
head(bmw_2014_zoo_weekly)
```

It is also possible to apply various transformations to the data.

Suppose we have a time series with time stamps $i = 0, \ldots, I$,
where $x_0$ refers to the starting date for the API call specified by `start_date`
and $x_I$ refers to the end point specified by `end_date`.

Possible values for the `transform` argument are

* none: leave the data as it is
* diff: shows the row - on - row change; 
  $$ 
    x^{*}_i = x_i - x_{i-1}
  $$
  
* rdiff: shows the relative row - on - row change; 
  $$ x^{*}_i = \dfrac{(x_i - x_{i-1})}{x_{i-1}} $$
  
* normalize: set starting value at 100; 
  $$ x^{*}_i = \dfrac{x_i}{x_0} \cdot 100 $$
  
* cumul: shows the cumulative sum; 
  $$ x^{*}_i =  x_i + x_{i-1} + x_{i-2} + \ldots + x_0 $$
  
* rdiff_from: shows ratio between the latest point and an earlier point; 
  $$ x^{*}_i = \dfrac{(x_I - x_{i})}{x_{i}} $$

Furthermore, you can select single columns of the data. 
If we want the returns of the closing prices (fourth column) of 2014 for BMW 
we have to call the Quandl function like this

```{r returnsclosing}
bmw_2014_returns_closing <- Quandl("GOOG/FRA_BMW.4",
                                   start_date = "2014-01-01", end_date = "2014-12-31",
                                   sort = "asc", type = "zoo", transform = "rdiff")

plot(bmw_2014_returns_closing, main = "BMW closing price returns 2014",
     ylab = "Returns", xlab = "Date")
summary(bmw_2014_returns_closing)
```

Finally, you can also get meta data. 
The only thing needed to receive this information is to switch the `meta` argument 
from **FALSE** to **TRUE**.

```{r meta}
bmw_2014_zoo_meta <- Quandl("GOOG/FRA_BMW", start_date = "2014-01-01", end_date = "2014-12-31",
                      sort = "asc", type = "zoo", meta = TRUE)
str(bmw_2014_zoo_meta, "meta")
```

The `meta` attribute of the object `bmw_2014_zoo_meta` is a list with 9 entries, such as frequency, name, description and so on.
Assuming that we are interested in an extended description of BMW we can get this with

```{r desc, eval = FALSE}
attr(bmw_2014_zoo_meta,"meta")$description
```

```{r cattmp, echo = FALSE}
tmp <- "Bayerische Motoren Werke AG is a German holding company and automobile manufacturer that 
focuses on the automobile and motorcycle markets. It divides its activities into the
three main segments: Automobiles, Motorcycles and Financial Services.
It owns three brands: BMW, MINI and Rolls-Royce. Its BMW automobile range
encompasses the 1 Series, including three-door, five-door, coupe and convertible models;
the 3 Series, including sedan, touring, coupe and convertible models;
the 5 Series, available in sedan and touring models;
the 6 Series, available as a coupe or convertible;
the 7 Series large sedan; the Z4 roadster and coupe;
the sports utility vehicles, X3, X5 and X6 and M models, such as M3, M5 and M6.
It also offers cars under the MINI brand and motorcycles under the BMW brand.
The Rolls-Royce brand offers three luxury cars, Phantom, Coupe and Ghost.
It has producing, assembly, service and sales subsidiaries throughout the world.
In January 2013, it sold its Husqvarna brand."
cat(tmp)
```