```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup', fig.width = 12, fig.height = 7, fig.align = "center")
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
library(Quandl)
Quandl.auth("x81naq-zMUpwM9fzkhYq")
Sys.setlocale(category = "LC_ALL", locale = "en_US.utf8")
# end setup chunk
```

# Downloading Data from Quandl Databases

The workhorse is the `Quandl()` function.
```{r quandlhelp, eval = FALSE}
Quandl(code, type = c("raw", "ts", "zoo", "xts", "timeSeries"), start_date,
  end_date, transformation = c("", "diff", "rdiff", "normalize", "cumul",
  "rdiff_from"), collapse = c("", "daily", "weekly", "monthly", "quarterly",
  "annual"), sort = c("desc", "asc"), meta = FALSE,
  authcode = Quandl.auth(), ...)
```

You can start downloading data by only using the `code` argument.
Codes can be found on the website of [Quandl](https://www.quandl.com) 
or you can query the databases directly within `R`. (see chapter 1.4).
Suppose we want the data for the automobile manufacturer *BMW* from Frankfurt Stock Exchange
using Google Finance as database.

```{r data}
bmw <- Quandl("GOOG/FRA_BMW")
```

```{r data1}
str(bmw)
```

```{r data2}
head(bmw)
```

```{r data3}
tail(bmw)
```

```{r data4}
summary(bmw)
```