```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md', fig.align = "center")
opts_chunk$set(prompt=TRUE, comment='', results='markup')
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
library(Quandl)
Quandl.auth("x81naq-zMUpwM9fzkhYq")
Sys.setlocale(category = "LC_ALL", locale = "en_US.utf8")
births <- Quandl("INSEE/62_001641602_M", type = "ts")
# end setup chunk
```

# `fArma` package

Install and/or load the library with the following commands.

```{r fArma, message=FALSE, eval = 2}
install.packages("fArma") # only necessary if package has not been installed yet
library(fArma)
```

We will use the `armaFit()` function from the `fArma` package for fitting ARMA models to historical time series.

```{r armaFit, eval = FALSE}
armaFit(formula, data, method = "ML")
# additional arguments removed
```

With `formula` argument one can specify which type of ARMA model should be fitted to `data`, which is the time series. 
Mandatory argument `formula` can be set in a `~arma(p,q)` style with the AR order \\(p\\) and the MA order \\(q\\).
Using the birth rates time series from the previous chapter one can fit a ARMA(1,1) to the data with the following line of code.
```{r birthsarma}
births_arma <- armaFit(formula = ~arma(1,1), data = births, method = "ML")
class(births_arma)
```

Applying the `summary` function to the `births_arma` object, which has class `fARMA`, by default gives an overview about the results
of the model estimation and produces some plots which can be used to interpret the goodness of fit.

```{r birthsarma_sum, fig.show = 'hold'}
summary(births_arma)
```


One can also forecast the time series with the `predict()` function. By default ten values are predicted.

```{r predictfun}
predict(births_arma)
```