```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup', fig.width = 12, fig.height = 7, fig.align = "center")
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
library(Quandl)
Quandl.auth("x81naq-zMUpwM9fzkhYq")
Sys.setlocale(category = "LC_ALL", locale = "en_US.utf8")
bmw <- readRDS("BMW2014.rds")
# births <- Quandl("INSEE/62_001641602_M", type = "ts")
# end setup chunk
```

# plotly Package
Yo can create easily interactive graphics with the help of the [`plotly`](https://plot.ly/r/) package.
```{r plotlyload, message = FALSE, warning = FALSE}
library(plotly)
```

Using plotly is free if you permit them to publish your plots on their website.
Nevertheless, you have to create an account and register it in the `R` session.

A starting guide for using the `plotly` package in `R` can be found [here](https://plot.ly/r/getting-started/).

```{r plotlyreg, echo = FALSE}
Sys.setenv("plotly_username"="anre005")
Sys.setenv("plotly_api_key"="ma3oawp8wd")
```

```{r plotlyreg1, eval = FALSE}
Sys.setenv("plotly_username"="YOUR_USERNAME")
Sys.setenv("plotly_api_key"="YOUR_API_KEY")
```

Let's take our `ggplot2` plot we have created in the previous section. 
Turning this into interactive graphic is very simple thanke to `ggplotly()` function.
```{r plotly1, results = "asis"}
p <- autoplot.zoo(bmw_2014_xts, 
                  main = "BMW OHLC plot with ggplot2",
                  facets = NULL) + xlab("") +  facet_free()
gg <- ggplotly(p)
gg
```

It is also easy to plot single time series, e.g. the traded volume per day for *BMW*, and even to annotate the plot.
The help page of the `plot_ly()` function tells us that the data should be a `data.frame`. 
Again we use our *BMW* `data.frame` from chapter 1.

```{r plotlyann, results='asis'}
# find the maximum volume
max_vol <- max(bmw[,"Volume"])

# find the index (rownumber) the maximum volume occurs
ind <- which(bmw[,"Volume"] == max_vol)

# find the corresponding date
date_max_vol <- bmw[ind,"Date"]

# plot Volume vs. Date
p <- plot_ly(bmw, x = Date, y = Volume, type = "bar")

# finally, add annotation
layout(p, annotations = list(x = date_max_vol, y = max_vol,
                             text = "Maximum Volume", showarrow = T))
```
