```{r knitsetup, echo=FALSE, results='hide', warning=FALSE, message=FALSE, cache=FALSE}
opts_knit$set(base.dir='./', fig.path='', out.format='md')
opts_chunk$set(prompt=TRUE, comment='', results='markup', fig.align = "center")
# See yihui.name/knitr/options for more Knitr options.
##### Put other setup R code here
Sys.setlocale(category = "LC_ALL", locale = "en_US.utf8")

# end setup chunk
```

# `stl()` function

```{r stl_main, eval = FALSE}
stl(x, s.window = "periodic")
# additional arguments removed
```

with the two mandatory arguments `x`, for the time series data, and `s.window` chosen as *periodic* assuming that the seasonal pattern is constant through time. On the help page of the function is mentioned that `x` should be a `ts` object.

More about the theory behind this function can be found [here](http://cs.wellesley.edu/~cs315/Papers/stl%20statistical%20model.pdf).

As an example we analyze monthly birth rates data for France
from the *National Institute of Statistics and Economic Studies (France)* database.

```{r birthratefrance}
births <- Quandl("INSEE/62_001641602_M", type = "ts")
plot(births)
```

It is obvious that the birth rates time series exhibits a seasonal pattern and a trend component.

```{r salesstl}
births_stl <- stl(births, s.window = "periodic")
# s.window = "periodic" means that we assume the seasonal pattern is constant through time

plot(births_stl)
```

`stl()` function returns a matrix with the seasonal, trend and remainder component.
```{r}
stl_mat <- births_stl$time.series
head(stl_mat)
```